This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-08 article.tex
Fixed an off-by-one error.

{\fontfamily{jkpvos}\selectfont\begin{center}
\begin{minipage}{0.8\hsize}\small
Thus=---thus=, my fellow-labourers= and associates= in this great harvest of our learning, now ripening before our eyes=; thus it is=, by slow steps= of casual increase, that our knowledge physical, metaphysical, physiological, polemical, nautical, mathematical, \ae{}nigmatical, technical, biographical, romantical, chemical, obstetrical, and polyglottical, with fifty other branches= of it, (most of 'em ending as= these do, in ical) have for these four last centuries= and more, gradually been creeping upwards= towards that Akme of their perfections=, from which, if we may form a conjecture from the advances= of these last \thepage~pages=, we cannot possibly be far off.
\end{minipage}
\end{center}}

>>>>

{\fontfamily{jkpvos}\selectfont\begin{center}
\begin{minipage}{0.8\hsize}\small
Thus=---thus=, my fellow-neighbours= and associates= in this= great harvest of our learning, now ripening before our eyes=; thus= it is=, by slow steps= of casual increase, that our knowledge physical, metaphysical, physiological, polemical, nautical, mathematical, \ae{}nigmatical, technical, biographical, romantical, chemical, obstetrical, and polyglottical, with fifty other branches= of it, (most of 'em ending as= these do, in ical) have for these four last centuries= and more, gradually been creeping upwards= towards= that Akme of their perfections=, from which, if we may form a conjecture from the advances= of these last \pgfmathparse{int(\thepage + 1)}\pgfmathresult~pages=, we cannot possibly be far off.
\end{minipage}
\end{center}}
